MLCommons Earthquake Science Benchmark

### 2022-02-25 paper-capstone-earthquake.tex

\TODO{Add your personal computers to this table \url{https://github.com/Data-ScienceHub/mlcommons-science/issues/37}}
\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:desktops}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|l|l|r|r|r|l|r|l|l|l|}
        \hline
        See also & 
        Organization   & 
        Machine                         &
        OS & 
        \rot{Processors~} &
        \rot{Core~} & 
        \rot{Threads~} & 
        GPUs             & 
        \rot{\makecell{Memory\\/Device}} &  
        \rot{GPU/Device} & 
        \rot{No. of nodes~} & 
        Commissioned \\ 
        \hline
        \hline
         Table \ref{tab:gcompute}   & 
         Gregor    & 
         5950X   &  
         Ubuntu 20.04&
         1 &   
         16 & 
         32 &
         \href{https://www.gigabyte.com/Graphics-Card/GV-N307TGAMING-OC-8GD#kf}{GIGABYTE Gaming RTX 3070TI}  & 
         8GB & 
         2 &
         1 &
         Sep 2021   \\
            & 
            &
            &
            &
            & 
            &  
            &   
         \href{https://rog.asus.com/us/graphics-cards/graphics-cards/rog-strix/rog-strix-rtx3090-o24g-gaming-model/}{ASUS ROG Strix RTX 3090} & 
         24GB & 
         & 
         & 
         Feb 2022   \\
         \hline
         \ref{sec:tcomputer}   & Thomas.A  & i7-8750H & Win11 Pro  & 1 &   ? & ? & NVIDIA GeForce RTX 2070 with Max-Q Design  & 16GB & 1 & 1 & 2019   \\
         \hline
         \ref{sec:t2computer}   & Thomas.B  & i7-7700HQ &  Win11 Pro &1 & ? & ? &  NVIDIA GeForce GTX 1060  & 16GB & 1 & 1 & 2017   \\
         \hline
         Table \ref{tab:rcompute} & 
         Rob & 
         5900HX & 
         Win11 Pro & 
         1 & 
         8 & 
         16 & 
         NVIDIA RTX 3080 &  
         16GB & 
         1 & 
         1 & 
         11/25/2021 \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

>>>>

\TODO{Add your personal computers to this table \url{https://github.com/Data-ScienceHub/mlcommons-science/issues/37}}
\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:desktops}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|l|l|r|r|r|l|r|l|l|l|}
        \hline
        See also & 
        Organization   & 
        Machine                         &
        OS & 
        \rot{Processors~} &
        \rot{Core~} & 
        \rot{Threads~} & 
        GPUs             & 
        \rot{\makecell{Memory\\/Device}} &  
        \rot{GPU/Device} & 
        \rot{No. of nodes~} & 
        Commissioned \\ 
        \hline
        \hline
         Table \ref{tab:gcompute}   & 
         Gregor    & 
         5950X   &  
         Ubuntu 20.04&
         1 &   
         16 & 
         32 &
         \href{https://www.gigabyte.com/Graphics-Card/GV-N307TGAMING-OC-8GD#kf}{GIGABYTE Gaming RTX 3070TI}  & 
         8GB & 
         2 &
         1 &
         Sep 2021   \\
            & 
            &
            &
            &
            & 
            &  
            &   
         \href{https://rog.asus.com/us/graphics-cards/graphics-cards/rog-strix/rog-strix-rtx3090-o24g-gaming-model/}{ASUS ROG Strix RTX 3090} & 
         24GB & 
         & 
         & 
         Feb 2022   \\
         \hline
         \ref{sec:tcomputer}   & Thomas.A  & i7-8750H & Win11 Pro  & 1 &   ? & ? & \href{https://www.gigabyte.com/Laptop/AERO-15--RTX-20-Series#kf}{NVIDIA GeForce RTX 2070 with Max-Q Design}NVIDIA GeForce RTX 2070 with Max-Q Design  & 16GB & 1 & 1 & 2019   \\
         \hline
         \ref{sec:t2computer}   & Thomas.B  & i7-7700HQ &  Win11 Pro &1 & ? & ? &  NVIDIA GeForce GTX 1060  & 16GB & 1 & 1 & 2017   \\
         \hline
         Table \ref{tab:rcompute} & 
         Rob & 
         5900HX & 
         Win11 Pro & 
         1 & 
         8 & 
         16 & 
         \href{https://rog.asus.com/us/laptops/rog-strix/2021-rog-strix-scar-15-series/}{NVidia RTX 3080} &  
         16GB & 
         1 & 
         1 & 
         11/25/2021 \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}
